\documentclass[version=last,12pt,{"C:/Program Files/R/R-3.6.1/library/komaletter/rmarkdown/templates/pdf/resources/maintainersDelight"},]{scrlttr2}

% For Debuging the Layout  ----------------------------------------------------
% \LoadLetterOption{visualize}
% \showfields{head,address,location,refline,foot}
% \setkomafont{field}{\color{blue}}
% -----------------------------------------------------------------------------

\usepackage{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
% \usepackage[margin=1in]{geometry} interfers with the areaset in my lco_default
%\usepackage[margin=1in]{geometry}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfauthor={Phil Walker},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
% make links footnotes instead of hotlinks (default)
\renewcommand{\href}[2]{#2\footnote{\url{#1}}}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\makeatletter
\usepackage{graphicx}
% grffile has become a legacy package: https://ctan.org/pkg/grffile
\IfFileExists{grffile.sty}{%
\usepackage{grffile}
}{}
% set default figure placement to htbp
\def\fps@figure{htbp}
\setkomavar{signature}{Phil Walker}
\makeatother











\setkomavar{subject}{Head of Demand and Inventory Planning/Operational Planning - SML NA}
\setkomavar{fromname}{Phil Walker}
\setkomavar{fromaddress}{5082 Garden Village Ct, Apt C\\Greensboro, NC 27410}


\begin{document}


\begin{letter}{Volvo Group\\7900 National Service Road\\Greensboro, NC 27409}
\opening{Dear Hiring Manager,}

\hypertarget{about-me}{%
\subsection{About Me}\label{about-me}}

I am an Industrial Engineer (IE) by education (BS and MS from Cal Poly)
who has had the good fortune to use my background in system driven
thinking to drive improvements throughout all of my roles. I cherish
opportunities to find creative solutions to the large scale challenges
and through the partnership with the end customer see those solutions
implemented and benefits realized. As both a Process Engineer for a
manufacturing company and a Sr.~Data Analyst within the financial
industry I have found that effective results come from partnering with
the end user and helping them to drive towards strong data driven
decisions.

\hypertarget{why-analytics-at-cone-health}{%
\subsection{Why Analytics at Cone
Health?}\label{why-analytics-at-cone-health}}

I am drawn to the opportunity that an advanced analytics resource has to
directly benefit not only Cone internally by improving the efficiency
and effectiveness of the business and clinical departments but also
passing along those benefits to patients and larger community. I am very
impressed with the focus and drive the team has find the cross section
between advanced analytical tools/techniques and the application of
those tools. As an Operations Analyst and Process Engineer, I loved when
I was encouraged and empowered to solve the hard problems and I see this
to be the vision of this role and team at large.

\hypertarget{why-me}{%
\subsection{Why Me?}\label{why-me}}

I believe I would be a strong asset to your team by bringing my industry
experience combined with my customer service mindset to the challenges
of the consultant role. Working at a manufacturing company, I succeeded
at balancing the needs of many different parties to solve long term
challenges, while still ensuring timely resolution of my day to day
responsibilities. As a Data Analyst, I spearheaded the cultural
transition within my team and across Operations to move from static and
often delayed snapshots of raw data towards data rich visualizations
with near live data, giving the opportunity for management to solve
problems long before they had significant consequences.

I am a creative problem solver whose brings to bear the disciplines of
IE and analytics to develop robust solutions. As I have in prior
positions, I continue to find and quickly learn tools and techniques to
help to provide better service to my customers. I learned SAS, R and
Tableau at my prior position when looking a address a gap and after
meeting those immediate needs I have found ways to harness those tools
to realize additional benefits.

\closing{Thank you for you consideration,}




\end{letter}

\end{document}
